### 2024-05-27 thesis/input_files/analysis.tex
May 27th 2024

Next, we extended the models to take into account the impact of two additional categorical variables
\begin{itemize}
    \item Is holiday: a binary variable for holidays, where holiday$=1$ and working day$=0$
    \item Day of week: an ordinal categorical variable corresponding to the day of the week, e.i.\ Monday$=0$,$\dots$, Sunday$=6$
\end{itemize}
Table \ref{tab:energy_chart_de_additional_predictors} reports the model scores on the German data while Table \ref{tab:energy_chart_ch_additional_predictors} is the one corresponding to the Suisse data.

@@

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in Germany (2021)}
\label{tab:secures_met_de}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{llllllllll}
\toprule
Quantile & Gaussian RBF & Laplacian & Matern 1.5 & Matern 2.5 & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
\midrule
0.1 & 0.028057 & \textbf{0.027483} & 0.028236 & 0.028257 & 0.028261 & 0.028277 & 0.028276 & 0.028146 & 0.028004 \\
0.2 & 0.047118 & \textbf{0.046051} & 0.047531 & 0.047544 & 0.047569 & 0.047595 & 0.047596 & 0.047353 & 0.047025 \\
0.3 & 0.060366 & \textbf{0.058739} & 0.060892 & 0.060940 & 0.060962 & 0.060988 & 0.060984 & 0.060654 & 0.060209 \\
0.4 & 0.068344 & \textbf{0.066347} & 0.068952 & 0.069022 & 0.069054 & 0.069104 & 0.069101 & 0.068634 & 0.068202 \\
0.5 & 0.071450 & \textbf{0.069118} & 0.072188 & 0.072250 & 0.072285 & 0.072331 & 0.072330 & 0.071807 & 0.071359 \\
0.6 & 0.068821 & \textbf{0.067098} & 0.069454 & 0.069526 & 0.069571 & 0.069615 & 0.069613 & 0.069157 & 0.068780 \\
0.7 & 0.061150 & \textbf{0.059972} & 0.061382 & 0.061410 & 0.061427 & 0.061442 & 0.061442 & 0.061281 & 0.060990 \\
0.8 & 0.047147 & \textbf{0.046457} & 0.047325 & 0.047331 & 0.047340 & 0.047348 & 0.047349 & 0.047247 & 0.047056 \\
0.9 & 0.026646 & 0.026343 & 0.026749 & 0.026757 & 0.026763 & 0.026772 & 0.026772 & \textbf{0.026282} & 0.026628 \\ 
\midrule
CRPS & 0.053233 & \textbf{0.051956} & 0.053634 & 0.053671 & 0.053693 & 0.053719 & 0.053718 & 0.053395 & 0.053139 \\
\bottomrule
\end{tabular}
\end{adjustbox}
\end{table}

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in Austria (2021)}
\label{tab:secures_met_at}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{llllllllll}
\toprule
Quantile & Gaussian RBF & Laplacian & Matern 1.5 & Matern 2.5 & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
\midrule
0.1 & 0.024309 & \textbf{0.023882} & 0.024316 & 0.024611 & 0.029367 & 0.029462 & 0.027319 & 0.029459 & 0.027816 \\
0.2 & 0.041028 & \textbf{0.040318} & 0.040987 & 0.041487 & 0.048510 & 0.048716 & 0.046164 & 0.048714 & 0.045879 \\
0.3 & 0.052597 & \textbf{0.051643} & 0.052548 & 0.052972 & 0.062242 & 0.062561 & 0.059133 & 0.062548 & 0.058454 \\
0.4 & 0.058803 & \textbf{0.057676} & 0.058841 & 0.059078 & 0.070210 & 0.070577 & 0.067914 & 0.070567 & 0.066335 \\
0.5 & 0.060846 & \textbf{0.059441} & 0.060912 & 0.061541 & 0.073399 & 0.073782 & 0.071616 & 0.073764 & 0.069574 \\
0.6 & 0.059336 & \textbf{0.057820} & 0.059237 & 0.059930 & 0.070817 & 0.071157 & 0.070249 & 0.071134 & 0.066970 \\
0.7 & 0.053937 & \textbf{0.052402} & 0.053949 & 0.054372 & 0.062453 & 0.062688 & 0.062970 & 0.062675 & 0.059419 \\
0.8 & 0.043366 & \textbf{0.042427} & 0.043364 & 0.043510 & 0.049024 & 0.049150 & 0.049737 & 0.049147 & 0.046662 \\
0.9 & 0.026727 & \textbf{0.026227} & 0.026645 & 0.026817 & 0.029516 & 0.029601 & 0.030097 & 0.029598 & 0.027986 \\
\midrule
CRPS & 0.046772 & \textbf{0.045760} & 0.046755 & 0.047146 & 0.055060 & 0.055299 & 0.053911 & 0.055290 & 0.052122 \\
\bottomrule
\end{tabular}
\end{adjustbox}
\end{table}
From our tables, it can be concluded that the absolute Laplacian kernel is the one fitting best to the characteristics of load data.
Additionally, we can conclude that our results are in line with the ones published in \cite{he2017short}. In that study, similarly to what we did in this subsection, the authors carried out a comparitive study concerning the choice of kernels in KQR. Nevertheless notice, that the set of kernel we considered in our study is larger than the one presented in \cite{he2017short}.
Their paper showed evidence of the superiority of the Gaussian RBF among their set of kernel functions. Analogously, we can see from Tables \ref{tab:secures_met_de}, \ref{tab:secures_met_ch} and \ref{tab:secures_met_at} that the Gaussian RBF is the second best in terms of pinball loss.

>>>>

Next, we extended the models to take into account the impact of two additional categorical variables
\begin{itemize}
    \item Is holiday: a binary variable for holidays, where holiday$=1$ and working day$=0$
    \item Day of week: an ordinal categorical variable corresponding to the day of the week, e.i.\ Monday$=0$,$\dots$, Sunday$=6$
\end{itemize}
Table \ref{tab:energy_chart_de_additional_predictors} reports the model scores on the German data while Table \ref{tab:energy_chart_ch_additional_predictors} is the one corresponding to the Swiss data.

@@

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in Germany (2021)}
\label{tab:secures_met_de}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllll}
        \toprule
        Quantile & \begin{tabular}[c]{@{}l@{}}Absolute\\ Laplacian\end{tabular} & \begin{tabular}[c]{@{}l@{}}Matern 0.5/\\ Laplacian\end{tabular} & Matern 1.5 & Matern 2.5 & \begin{tabular}[c]{@{}l@{}}Matern $\infty$/\\ Gaussian RBF\end{tabular} & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
        \midrule
        0.1 & 0.027483 & 0.027827 & 0.028236 & 0.028257 & 0.028057 & 0.028261 & 0.028277 & 0.028276 & 0.028146 & 0.028004 \\
        0.2 & 0.046051 & 0.046679 & 0.047531 & 0.047544 & 0.047118 & 0.047569 & 0.047595 & 0.047596 & 0.047353 & 0.047025 \\
        0.3 & 0.058739 & 0.059835 & 0.060892 & 0.060940 & 0.060366 & 0.060962 & 0.060988 & 0.060984 & 0.060654 & 0.060209 \\
        0.4 & 0.066347 & 0.067768 & 0.068952 & 0.069022 & 0.068344 & 0.069054 & 0.069104 & 0.069101 & 0.068634 & 0.068202 \\
        0.5 & 0.069118 & 0.070761 & 0.072188 & 0.072250 & 0.071450 & 0.072285 & 0.072331 & 0.072330 & 0.071807 & 0.071359 \\
        0.6 & 0.067098 & 0.068276 & 0.069454 & 0.069526 & 0.068821 & 0.069571 & 0.069615 & 0.069613 & 0.069157 & 0.068780 \\
        0.7 & 0.059972 & 0.060783 & 0.061382 & 0.061410 & 0.061150 & 0.061427 & 0.061442 & 0.061442 & 0.061281 & 0.060990 \\
        0.8 & 0.046457 & 0.046944 & 0.047325 & 0.047331 & 0.047147 & 0.047340 & 0.047348 & 0.047349 & 0.047247 & 0.047056 \\
        0.9 & 0.026343 & 0.026554 & 0.026749 & 0.026757 & 0.026646 & 0.026763 & 0.026772 & 0.026772 & 0.026282 & 0.026628 \\
        \midrule
        CRPS & 0.051956 & 0.052825 & 0.053634 & 0.053671 & 0.053233 & 0.053693 & 0.053719 & 0.053718 & 0.053395 & 0.053139 \\
        \bottomrule
        \end{tabular}
\end{adjustbox}
\end{table}

\begin{table}[!ht]
    \centering
\caption{Pinball loss kernel comparison for load in Austria (2021)}
\label{tab:secures_met_at}
\begin{adjustbox}{width=\textwidth}
    \begin{tabular}{lllllllllll}
        \toprule
        Quantile & \begin{tabular}[c]{@{}l@{}}Absolute\\ Laplacian\end{tabular} & \begin{tabular}[c]{@{}l@{}}Matern 0.5/\\ Laplacian\end{tabular} & Matern 1.5 & Matern 2.5 & \begin{tabular}[c]{@{}l@{}}Matern $\infty$/\\ Gaussian RBF\end{tabular} & Linear & Periodic & Polynomial & Sigmoid & Cosine \\
        \midrule
    0.100000 & 0.023882 & 0.027901 & 0.024316 & 0.024611 & 0.024309 & 0.029367 & 0.029462 & 0.027319 & 0.029459 & 0.027816 \\
    0.200000 & 0.040318 & 0.046043 & 0.040987 & 0.041487 & 0.041028 & 0.048510 & 0.048716 & 0.046164 & 0.048714 & 0.045879 \\
    0.300000 & 0.051643 & 0.058812 & 0.052548 & 0.052972 & 0.052597 & 0.062242 & 0.062561 & 0.059133 & 0.062548 & 0.058454 \\
    0.400000 & 0.057676 & 0.066704 & 0.058841 & 0.059078 & 0.058803 & 0.070210 & 0.070577 & 0.067914 & 0.070567 & 0.066335 \\
    0.500000 & 0.059441 & 0.071401 & 0.060912 & 0.061541 & 0.060846 & 0.073399 & 0.073782 & 0.071616 & 0.073764 & 0.069574 \\
    0.600000 & 0.057820 & 0.067650 & 0.059237 & 0.059930 & 0.059336 & 0.070817 & 0.071157 & 0.070249 & 0.071134 & 0.066970 \\
    0.700000 & 0.052402 & 0.059061 & 0.053949 & 0.054372 & 0.053937 & 0.062453 & 0.062688 & 0.062970 & 0.062675 & 0.059419 \\
    0.800000 & 0.042427 & 0.047954 & 0.043364 & 0.043510 & 0.043366 & 0.049024 & 0.049150 & 0.049737 & 0.049147 & 0.046662 \\
    0.900000 & 0.026227 & 0.028459 & 0.026645 & 0.026817 & 0.026727 & 0.029516 & 0.029601 & 0.030097 & 0.029598 & 0.027986 \\
    \midrule
    CRPS & 0.045760 & 0.052665 & 0.046755 & 0.047146 & 0.046772 & 0.055060 & 0.055299 & 0.053911 & 0.055290 & 0.052122 \\
    \bottomrule
    \end{tabular}
\end{adjustbox}
\end{table}
From our tables, it can be concluded that the absolute Laplacian kernel is the one fitting best to the characteristics of load data.
Additionally, we can conclude that our results are in line with the ones published in \cite{he2017short}. In that study, similarly to what we did in this subsection, the authors carried out a comparitive study concerning the choice of kernels in KQR. Nevertheless notice, that the set of kernel we considered in our study is larger than the one presented in \cite{he2017short}.
Their paper showed evidence of the superiority of the Gaussian RBF among their set of kernel functions. Analogously, we can see from Tables \ref{tab:secures_met_de}, \ref{tab:secures_met_ch} and \ref{tab:secures_met_at} that the Gaussian RBF is the second best in terms of pinball loss.
